Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-21 WSSSPE2_report/WSSSPE2_review.tex
Section 7: Add line breaks. No change in content.
Section 7: Intro: add a word.

This group, with just three papers but a large amount of interest and participation from attendees,
focused on the institutional, social, and cultural mechanisms encourage the creation
and maintenance of shared software, in the context of what now exists but focusing
on what mechanisms are desired and how we might achieve them.

>>>>

This group, with just three papers but a large amount of interest and
participation from attendees, focused on the institutional, social, and cultural
mechanisms that encourage the creation and maintenance of shared software, in the
context of what now exists but focusing on what mechanisms are desired and how
we might achieve them.
